---
title: "hw0"
format:
    html: 
       embed-resources: true
editor: visual
execute:
  echo: false
---

## Part 1

-   Write a Quarto document that defines variables $a=1, b=3, c=2$ and print out the solutions to $f(x) = ax^2+bx+c=0$.

```{r}
# Define the coefficients
a <- 1
b <- 3
c <- 2

# Calculate the discriminant
D <- b^2 - 4*a*c

# Check if the roots are real
if (D >= 0) {
  root1 <- (-b + sqrt(D)) / (2*a)
  root2 <- (-b - sqrt(D)) / (2*a)
  if (D == 0){
    cat("There is only one real root:",root1,"\n")
  }else{
    cat("The real roots are:", root1, "and", root2, "\n")
  }
} else {
  cat("There are no real roots.\n")
}
```

Since $ax^2+bx+c=0$ is a quadratic equation with one unknown variable, we can first calculate the discriminant $D$ which is given by the formula $D=b^2-4ac$ . The roots are then calculated using $\frac{{-b \pm \sqrt{D}}}{2a}$. If $D$ is less than 0, real roots do not exist. If $D$ is equal to 0, there is one real root. If $D$ is larger than 0, there are two distinct real roots.

## Part 2

-   Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$ to verify the solutions.

```{r}
# define xlim
x <- seq((root2-1), (root1+1), by=0.05)

# define f(x)
y <- a*x^2 + b*x + c

# draw a scatter plot
plot(x, y, type='p', pch = ".",cex = 3)

# Add horizontal line at y=0
abline(h=0, col="red")

# Add vertical lines at x = root1 and x = root2
abline(v = root1, col = "blue", lty=2) 
abline(v = root2, col = "green", lty=2)
```

I am plotting $f(x)=ax^2+bx+c$ over a range of $x$ values that extend a little beyond its real roots. Additionally, I include a red horizontal line at $y=0$ to easily identify where the function crosses the x-axis, which are the roots of the equation $f(x)=0$. I also add vertical dashed lines at the x-coordinates corresponding to the two roots, color-coded in blue and green, to visually indicate the solutions to $f(x)$. Since the intersections of the vertical lines and the horizontal line lie on the function curve, the solutions are correct.
